A Systematic Review of the Use of the ESM Methodology in Education

### 2020-09-04 paper_draft.Rmd
minor edits to manuscript
more update for the elements of coding, will go into further depth of explaining the elements

## Construct
What is the focus of the study? 
There are many different types of constructs that researchers used ESM to investigate:
**list**

@@

## Sample Size

@@

## Length of Signaling Period (study length)

@@

How did the researcher analysis the data.

>>>>

## Construct
We wanted to find out what the extent that the research literature has covered as the them of study. The constructs have a variable of depth, some coding for the construct were singular and had a single focus. Other articles investigate several constructs and are broad in the scope that they cover. 
What is the focus of the study? 
There are many different types of constructs that researchers used ESM to investigate:
**list**

@@

The main focus of participants were students, but there were others that included teachers or industry workers. 
## Sample Size

@@

## Length of Signaling Period (study length)
This is a determining factor for the

@@

How did the researcher analysis the data. Authors used different terms for similar analysis.
